Optimized Keyword Persistent Hash Maps for Clojure

### 2016-12-06 paper/paper.tex
restructure
remove paragraph

\paragraph{Abstract classes}
Clojure provides poor support for 
extending abstract classes. This meant
we either had to reimplement the abstract class,
which was often long, or use proxies, a less
elegant feature of Clojure.
%
We decided to use proxies to save effort, but we think it detracts
from the readability of the implementation.

\paragraph{Mutation}
Clojure does not expose plain Java variables, so several
style and performance decisions were made faithfully port
local loops with complicated mutation.
We decided to use Clojure's volatiles, which are variables
that guarantee ordering constraints (like a \texttt{volatile}
Java variable).

>>>>

%\paragraph{Abstract classes}
%Clojure provides poor support for 
%extending abstract classes. This meant
%we either had to reimplement the abstract class,
%which was often long, or use proxies, a less
%elegant feature of Clojure.
%%
%We decided to use proxies to save effort, but we think it detracts
%from the readability of the implementation.
%
\paragraph{Mutation}
Clojure does not expose plain Java variables, so several
style and performance decisions were made faithfully port
local loops with complicated mutation.
We decided to use Clojure's volatiles, which are variables
that guarantee ordering constraints (like a \texttt{volatile}
Java variable).
